Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-21 latex/article.tex
wip
pe

\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
isosurface on volumetric data has been widely investigated since the
seminal Marching-Cubes approach by Lorensen and
Cline~\cite{lorensen1987marching}. This approach being data parallel,
GPU implementation of this method is very efficient
\cite{tatarchuk2007real}. However, such technique generates a lot of
triangles which is not well suited to large digital data. Hence,
adaptive approaches have been proposed in order to optimize the
triangular mesh resolution to the object geometry or depending on the
viewpoint. In this topic, many solutions have been developed in
Computer
Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
The method developed by Lengyel \textit{et al.}
\cite{lengyel2010voxel} is the best suited to our needs.  However, it
was developed to visualize in real-time static or near static data and
present a complex CPU implementation.\todo{DC: rajouter une phrase par
  rapport à lengyel, Helene ? JP?}  In this paper we propose a GPU
pipeline inspired from this method.  It leaves the CPU free for other
tasks and avoids synchronization with the GPU.  Our high framerate
also allows this method to run in real-time on fully dynamic data.
The triangulation is controlled by a GPU LoD criterion that ensures
that triangles project onto more than one pixel, thus removing
geometrical aliasing.

@@

\sloppy In our context, we consider digital shapes (any subset of
$\Z^d$) and boundaries of digital shapes. We denote by $\DSh$ the
Gauss digitization of $\Shape$ in a $d-$dimensional grid with grid
step $h$, \emph{i.e.}  $\DSh \EqDef \{ \vz \in \Z^d,\, h\cdot\vz\in\Shape\}$. For such
digitized set $\DigShape\EqDef\DSh$, $\Body{\DigShape}{h}$ is a subset
of $\R^d$ corresponding to the union of hypercubes centered at $h\cdot
\vz$ for $\vz\in Z$ with edge length $h$. By doing so, both
$\partial\Shape$ and $\partial\Body{Z}{h}$ are topological boundary of
objects lying in the same space (See Fig. \ref{fig:notations}-b). Note
that the combinatorial digital boundary of $Z$ made of cells in a
cellular Cartesian complex (\emph{pointels}, \emph{linels}, {\em
  surfels}, \ldots), can be trivally embedded into $\R^d$ such that it
coincides with $\partial\Body{Z}{h}$.

\begin{figure}[t]{\small
    \begin{center}
      \subfigure[]{\begin{overpic}[width=5cm]{figs/integral2D_2}
          \put(42,28){$\times$}
          \put(46,31){$\vx$}
          \put(55,45){$B_R(\vx)$}
          \put(1,10){$\dS$}
          \put(20,10){$\Shape$}
      \end{overpic}}~~~~~~
      \subfigure[]{\begin{overpic}[width=5cm]{figs/notation_2}
          \put(44.5,25){$\vp$}
          \put(55,45){$B_R(\vx)$}
          \put(42,28.5){$\times$}
          \put(45,32.5){$\vx$}
          \put(45,16.5){$h$}
          %\put(88,39){$\Proj(p)$}
          \put(3,11){$\partial \Shape$}
          \put(15,7){$\partial \Body{\DigShape}{h}$}
      \end{overpic}}
      \vspace{-0.4cm}
    \end{center}}
    \caption{Integral invariant computation $(a)$ and
      notations $(b)$ in dimension 2 \cite{CVIU2014}.\label{fig:notations}}
\end{figure}

>>>>

\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
isosurface on volumetric data has been widely investigated since the
seminal Marching-Cubes approach by Lorensen and
Cline~\cite{lorensen1987marching}. This approach being data parallel,
GPU implementation of this method is very efficient
\cite{tatarchuk2007real}. However, such technique generates a lot of
triangles which is not well suited to large digital data. Hence,
adaptive approaches have been proposed in order to optimize the
triangular mesh resolution to the object geometry or depending on the
viewpoint. In this topic, many solutions have been developed in
Computer
Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
The method developed by Lengyel \textit{et al.}
\cite{lengyel2010voxel} is the best suited to our needs.  However, it
was only developed on CPU to visualize in real-time static or near
static data, combining octree with new Marching-Cubes configurations
to generate adaptive meshes. In this paper we propose a GPU pipeline
inspired from this method.  It leaves the CPU free for other tasks and
avoids synchronization with the GPU.  Our high framerate also allows
this method to run in real-time on fully dynamic data.  The
triangulation is controlled by a GPU LoD criterion that ensures that
triangles project onto more than one pixel, thus removing geometrical
aliasing.

@@

\sloppy In our context, we consider digital shapes (any subset $Z$ of
$\Z^d$) and boundaries of digital shapes $\partial Z$. We denote by $\DSh$ the
Gauss digitization of $\Shape$ in a $d-$dimensional grid with grid
step $h$, \emph{i.e.}  $\DSh \EqDef \{ \vz \in \Z^d,\, h\cdot\vz\in\Shape\}$. For such
digitized set $\DigShape\EqDef\DSh$, $\Body{\DigShape}{h}$ is a subset
of $\R^d$ corresponding to the union of hypercubes centered at $h\cdot
\vz$ for $\vz\in Z$ with edge length $h$. By doing so, both
$\partial\Shape$ and $\partial\Body{Z}{h}$ are topological boundary of
objects lying in the same space (See Fig. \ref{fig:notations}-b). Note
that the combinatorial digital boundary of $Z$ made of cells in a
cellular Cartesian complex (\emph{pointels}, \emph{linels}, {\em
  surfels}, \ldots), can be trivally embedded into $\R^d$ such that it
coincides with $\partial\Body{Z}{h}$.

\begin{figure}[t]{\small
    \begin{center}
      \subfigure[]{\begin{overpic}[width=5cm]{figs/integral2D_2}
          \put(42,28){$\times$}
          \put(46,31){$\vx$}
          \put(55,45){$B_R(\vx)$}
          \put(1,10){$\dS$}
          \put(20,10){$\Shape$}
      \end{overpic}}~~~~~~
      \subfigure[]{\begin{overpic}[width=5cm]{figs/notation_2}
          \put(44.5,25){$h \cdot \vz$}
          \put(55,45){$B_R(\vx)$}
          \put(42,28.5){$\times$}
          \put(45,32.5){$\vx$}
          \put(45,16.5){$h$}
          %\put(88,39){$\Proj(p)$}
          \put(3,11){$\partial \Shape$}
          \put(15,7){$\partial \Body{\DigShape}{h}$}
      \end{overpic}}
      \vspace{-0.4cm}
    \end{center}}
    \caption{Integral invariant computation $(a)$ and
      notations $(b)$ in dimension 2 \cite{CVIU2014}.\label{fig:notations}}
\end{figure}
